Enhancing Forecast Reconciliation: A Study of Alternative Covariance Estimators

### 2025-07-29 literature/paper_draft.qmd
Update paper_draft.qmd

```{r library}
library(ggplot2)
library(patchwork)
library(ReconCov)
library(dplyr)
library(tidyr)
library(fable)
library(fabletools)
library(feasts)
library(tsibble)

@@

# sim1_1 <- readRDS("./literature/lib/S4-2-1_T100_M10000_par.rds")
# sim1_2 <- readRDS("./literature/lib/S4-2-1_T300_M10000.rds")

@@

# sim3_1 <- readRDS("./literature/lib/S100-2-1_T50_M200_run1.rds")
# sim3_2 <- readRDS("./literature/lib/S100-2-1_T100_M200_run1.rds")
# 
# MSE1_1 <- transform_sim_MSE(sim1_1$MSE, F)
# MSE1_2 <- transform_sim_MSE(sim1_2$MSE, F)

@@

# MSE3_1 <- transform_sim_MSE(sim3_1$MSE, F)
# MSE3_2 <- transform_sim_MSE(sim3_2$MSE, F)
```

>>>>

```{r library}
library(ggplot2)
library(patchwork)
library(ReconCov)
library(dplyr)
library(tidyr)
library(fable)
library(fabletools)
library(feasts)
library(tsibble)
library(lubridate)

@@

sim1_1 <- readRDS("./literature/lib/S4-2-1_T100_M10000_par.rds")
sim1_2 <- readRDS("./literature/lib/S4-2-1_T300_M10000.rds")

@@

sim3_1 <- readRDS("./literature/lib/S100-2-1_T50_M200_run1.rds")
sim3_2 <- readRDS("./literature/lib/S100-2-1_T100_M200_run1.rds")

MSE1_1 <- transform_sim_MSE(sim1_1$MSE, F)
MSE1_2 <- transform_sim_MSE(sim1_2$MSE, F)

@@

MSE3_1 <- transform_sim_MSE(sim3_1$MSE, F)
MSE3_2 <- transform_sim_MSE(sim3_2$MSE, F)
```
